Technologies of Semantic WEB as an environment of application development and integration

### 2022-02-03 paper-aicts-cherkashin.tex
Added subsections for the examples.

In this section, three examples of application implementation are being presented.

@@

@@

\end{thebibliography}
\section{Online Resources}

The sources for the viewer are being developed at Github, URL:~\url{https://github.com/De17eon/GRL}.

>>>>

In this section, three examples of application implementation are being presented.  The first example is an MDA application in the synthesis of a Next-generation sequencing (NGS) investigation environment.  After the invention of methods of NGS and their introduction in practice of biological systems research, a new direction of molecular genetics is formed, which is referred to as \emph{metagenomics}.  The method allows biologists to describe a significant number of new groups of organisms at all taxonomic levels. A comprehensive review of present sequencing approaches and challenges is presented in~\cite{pere20}.

\subsection{Next-generation sequencing}
\label{sec:ngs-impl}

The aim of this R\&D is to develop software support of the processes of NGS analysis with techniques and software for a visual representation of the computational process of so-called amplicon analysis so that domain specialists would be able to compose computational pipelines, which are executed on distributed heterogeneous computing resources (clouds).  The visual models, later, are to be used for organizing the computational process and data store and articular retrieval services.

The tools are based on dataflow representation of various stages of NGS standard operation procedures (SOPs) in Rapidminer studio Java application.  /Speak about biologists involvement in the process of dataflow diagram construction. Analogous soft and integration with them/.

\subsection{Education document authoring}
\label{sec:doc-impl}

\subsection{Web GIS on the base of a knowledge graph}
\label{sec:gis-impl}

@@

\section*{Conclusion}

@@

\end{thebibliography}
% \section{Online Resources}

% The sources for the viewer are being developed at Github, URL:~\url{https://github.com/De17eon/GRL}.
